Methods paper for erosion

### 2017-10-19 docs/methods/erosion_methods.tex
worked on numerics section of methods paper

To model erosion, we the normal velocity is prescribed to be
proportional to the absolute value of the shear stress.  The constant of
proportionality sets the time scale, and we set its value to be -1
\begin{align}
  \dot{\xx}(t) = \abs{\tau} \nn.
  \label{eqn:bodyEvolution}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
same procedure used for the shear stress.  We start by computing the
pressure of the double-layer potential for $\xx \in \Omega$ and add the
appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
is
\begin{align}
  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
\end{align}
To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
as $\xx$ tends to $\xx_0$.  The limiting value is given
by~\cite{qua-bir2014a}
\begin{align*}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
\end{align*}
The pressure due to the Stokeslets is
\begin{align*}
  p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
\end{align*}
and the pressure due to the rotlets is zero.  Therefore, the pressure is
\begin{equation}
\label{eqn:pressureDLP}
\begin{aligned}
  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
              p^{S}(\xx), && \xx \in \bd\Omega.
\end{aligned}
\end{equation}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
Each body is represented with at $N_\iin$ points as the Fourier series
\begin{align*}
  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta},
    \quad k=1,\ldots,M.
\end{align*}
The exterior geometry is represented with a Fourier series using
$N_\out$ points.  Derivatives of the shape are computed in Fourier space
\begin{align*}
  \frac{d\xx^k(\theta)}{d\theta} = 
    \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta},
    \quad k=1,\ldots,M.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
Integrals that need to be approximated are the double-layer potential
for for the velocity at target points both off the
boundary~\eqref{eqn:velocityDLP} and on the boundary~\eqref{eqn:DLP},
the shear stress~\eqref{eqn:shearStressDLP}, the
vorticity~\eqref{eqn:vorticityDLP}, the pressure both off and on the
boundary~\eqref{eqn:pressureDLP}, the drag~\eqref{eqn:drag}, and the
resistivity.   The shear stress, pressure, and drag must also be
computed using quadrature, and this can be interpreted as a
post-processing step once the density function, Stokeslets, and rotlets
are computed.

All the integrands, except for the resistivity, are periodic, so the
trapezoid rule guarantees spectral accuracy~\cite{tre-wei2014}.
However, before the trapezoid rule can be applied, singularity
subtraction and odd-even integration~\cite{sid-isr1988} must be used.
In addition, when the target point is near $\bd\Omega$, a near-singular
integration scheme must be used.

\todo[inline]{Organize as first doing points on the boundary (velocity,
shear stress, pressure, drag) and the points off the boundary (velocity,
vorticity, pressure, resistivity)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Velocity}
To numerically evaluate the completed double-layer
potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
be the total number of discretization points of $\bd\Omega$.  The
double-layer potential in~\eqref{eqn:DLP} is discretized with the
trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}, \quad i=1,\ldots,N,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align*}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2},
\end{align*}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
replaced with the limiting value of the double-layer potential
\begin{align*}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
\end{align*}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
vector at $\xx \in \bd\Omega$.  The strengths of the
Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
also discretized with the trapezoid rule.  Applying this discretization
strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
needs to be solved is
\begin{equation}
  \label{eqn:completed_BIE_discretized}
  \begin{aligned}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} +
      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) +
      \sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) + 
      \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j), \\
    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
      \Delta s_i \\ 
    \mu_k &= \sum_{\xx_i \in \gamma_k}
      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
  \end{aligned}
\end{equation}
for $i=1,\ldots,N$, $k=1,\ldots,M$.  Since all the integrands are smooth
and periodic, by using the trapezoid rule, we are guaranteed that the
numerical solutions converges to the true solution with spectral
accuracy.

@@

To compute the velocity at an interior point $\xx \in \Omega$, the
integrand is periodic and smooth, so the trapezoid rule rule achieves
spectral accuracy.  Therefore, the velocity at a target points $\xx \in
\Omega$ is approximate by
\begin{align*}
  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
\end{align*}
If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
where $N_\tar$ is large, the FMM is used to reduce the complexity from
$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Stress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  However, the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
\rightarrow \xx$.  The singularity strength can be reduced since the
velocity corresponding to a constant density function is
constant~\cite{poz1992}.  Therefore, the deformation tensor of the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
to achieve spectral accuracy, we apply odd-even
integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
the double-layer potential at a discretization point $\xx_i$ on body
$\gamma_k$, with $i$ being odd, is approximated as
\begin{align*}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
\end{align*}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets is given in
equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
computed by computing the deformation tensor in the normal direction,
and taking the inner product with the tangent direction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vorticity}
Since the vorticity is equivalent to the shear stress on $\bd\Omega$, we
only need to compute the vorticity at target points at interior points
$\xx \in \Omega$.  This is done with the trapezoid rule by computing
\begin{align*}
  \omega(\xx_i) = \sum_{j=1}^N K_\omega (\xx_i,\xx_j) \cdot \eeta_j 
    \Delta s_j,
\end{align*}
where
\begin{align*}
  K_\omega (\xx,\yy) =  -\frac{\rr}{\pi}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4}.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
For the pressure, the double-layer potential is equivalent to
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}

>>>>

To model erosion, we the normal velocity is prescribed to be
proportional to the absolute value of the shear stress.  The constant of
proportionality sets the time scale, and we set its value to be 1
\begin{align}
  \dot{\xx}(t) = \abs{\tau} \nn.
  \label{eqn:bodyEvolution}
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
same procedure used for the shear stress.  We start by computing the
pressure of the double-layer potential for $\xx \in \Omega$ and add the
appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
is
\begin{align}
  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
    \label{eqn:pressureDLP}
\end{align}
To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
as $\xx$ tends to $\xx_0$.  The limiting value is given
by~\cite{qua-bir2014a}
\begin{align*}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
\end{align*}
The pressure due to the Stokeslets is
\begin{align*}
  p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
\end{align*}
and the pressure due to the rotlets is zero.  Therefore, the pressure is
\begin{align*}
  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
              p^{S}(\xx), && \xx \in \bd\Omega.
\end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Resistivity}
\begin{align}
  some equation
  \label{eqn:resistivity}
\end{align}

In Section~\ref{sec:spatial_discretization}, we describe how the
geometry is represented.  Then, Sections~\ref{sec:on_boundary}
and~\ref{sec:off_boundary} describe how the velocity and other
quantities of interest are computed at points on and off the boundary,
respectively.  Then, in Section~\ref{sec:thetaL}, methods used to update
the shape are described.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{sec:spatial_discretization}
Each body is represented with at $N_\iin$ points as the Fourier series
\begin{align*}
  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta},
    \quad k=1,\ldots,M.
\end{align*}
The exterior geometry is represented with a Fourier series using
$N_\out$ points.  Derivatives of the shape are computed in Fourier space
\begin{align*}
  \frac{d\xx^k(\theta)}{d\theta} = 
    \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta},
    \quad k=1,\ldots,M.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature: On Boundary Calculations} 
\label{sec:on_boundary}
We start by discussing the quadrature methods that are used to compute
the velocity~\eqref{eqn:DLP}, shear stress~\ref{eqn:shearStressDLP},
pressure~\eqref{eqn:pressureDLP}, and drag~\eqref{eqn:drag} at target
points on the boundary of the domain.  The velocity on $\bd\Omega$ is
required to solve the integral equation~\eqref{eqn:completed_BIE} for
the density function, Stokeslets and rotlets.  Once these are computed,
computing the shear stress, pressure, and drag is a post-processing
step.

All these integrals involve integrands that are both periodic and
smooth, so the trapezoid rule guarantees spectral
accuracy~\cite{tre-wei2014}.  However, before the trapezoid rule can be
applied, singularity subtraction and odd-even
integration~\cite{sid-isr1988} must be used.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Velocity}
To numerically evaluate the completed double-layer
potential~\eqref{eqn:completed_BIE}, we define $N = MN_\iin + N_\out$ to
be the total number of discretization points of $\bd\Omega$.  The
double-layer potential in~\eqref{eqn:DLP} is discretized with the
trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}, \quad i=1,\ldots,N,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align*}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2},
\end{align*}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the
double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is
replaced with the limiting value of the double-layer potential
\begin{align*}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)),
\end{align*}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent
vector at $\xx \in \bd\Omega$.  The strengths of the
Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are
also discretized with the trapezoid rule.  Applying this discretization
strategy to~\eqref{eqn:completed_BIE}, the dense linear system that
needs to be solved is
\begin{equation}
  \label{eqn:completed_BIE_discretized}
  \begin{aligned}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
      \sum_{k=1}^M S[\llambda_k,\cc_k](\xx_i) \\
      &\hspace{40pt}
      +\sum_{k=1}^M R[\xi_k,\cc_k](\xx_i) 
      +\sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j), \\
    \llambda_k &= \sum_{\xx_i \in \gamma_k} \eeta(\xx_i) 
      \Delta s_i \\ 
    \mu_k &= \sum_{\xx_i \in \gamma_k}
      {(\xx_i^k - \cc_k)}^\perp \cdot \eeta(\xx_i^k) \Delta s_i^k,
  \end{aligned}
\end{equation}
for $i=1,\ldots,N$, $k=1,\ldots,M$.  Since all the integrands are smooth
and periodic, by using the trapezoid rule, we are guaranteed that the
numerical solutions converges to the true solution with spectral
accuracy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Stress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  However, the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy) = \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) +
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
\rightarrow \xx$.  The singularity strength can be reduced since the
velocity corresponding to a constant density function is
constant~\cite{poz1992}.  Therefore, the deformation tensor of the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
to achieve spectral accuracy, we apply odd-even
integration~\cite{sid-isr1988}.  That is, the deformation tensor due to
the double-layer potential at a discretization point $\xx_i$ on body
$\gamma_k$, with $i$ being odd, is approximated as
\begin{align}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_k}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_k \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
  \label{eqn:stressOddEven}
\end{align}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets is given in
equation~\eqref{eqn:shearStressSR}, and then the shear stress can be
computed by computing the deformation tensor in the normal direction,
and taking the inner product with the tangent direction.

\todo[inline]{discuss how we handle jump condition ... Fourier
differentiation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
Similar to the shear stress, the singularity of the pressure
corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
too strong for the trapezoid rule to be directly applied.  Therefore, we
again subtract a constant density function and write the pressure as
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}
Then, identical to how the shear stress is
computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
evaluate this layer potential for pressure.

\todo[inline]{discuss how we handle jump condition ... Fourier
differentiation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature: Off Boundary Calculations} 
\label{sec:off_boundary}
To analyze the flow, we compute quantities at target points that are in
the interior of the domain.  In particular, we develop numerical methods
to compute the velocity~\eqref{eqn:velocityDLP},
pressure~\eqref{eqn:pressureDLP}, vorticity~\eqref{eqn:vorticityDLP} and
resistivity~\eqref{eqn:resistivity}.

Similar to when the target points are on the boundary of the domain, all
the integrals, except for the resistivity, involve integrands that are
both periodic and smooth.  However, when the target points are close to
the boundary of the domain, the integrand becomes nearly-singular, and
these large derivatives result in a loss of accuracy that needs to be
rectified.  We will be adopting a near-singular integration scheme that
allows us to compute all quantities of interest sufficiently close to
$\bd\Omega$ for the results we are untested in.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Near-singular integration}
To accurately compute quantities such as the velocity at points $\xx \in
\Omega$, we adopt a near-singular integration scheme entirely based on
upsampling.  Since we are only interested in computing the velocity and
vorticity for visualizing the flow, and the pressure is only required
far away from any boundary, only a finite amount of upsampling is
required to achieve an acceptable error.

Computing the velocity, pressure, and vorticity at a point $\xx \in
\Omega$ requires evaluating the layer potential
\begin{align*}
  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy,
\end{align*}
where $\phi$ is either the velocity, pressure, or vorticity, and the
kernel $K$ is in
equations~\eqref{eqn:velocityDLP},~\eqref{eqn:vorticityDLP},
and~\eqref{eqn:pressureDLP}.  This integral is approximated with a
trapezoid rule, which can be easily done with the $N$ points where the
density function has been solved
\begin{align}
  \phi(\xx) \approx \sum_{k=1}^N q_k K(\xx,\yy_k),
  \label{eqn:layerPotential}
\end{align}
where $q$ contains the quadrature weights, Jacobian, and density
function.  Based on numerical experiments, the error of the $N$-point
trapezoid rule is acceptable for points $\xx$ that are more than 5
arclength spacings from $\bd\Omega$.

For points that are closer than 5 arclength spacings to $\bd\Omega$, we
use an upsampled trapezoid rule.  The required upsampling of the
geometry and the density function is done with a Fourier interpolant.
To minimize the number of discretization points that are used to
approximate the layer potential~\eqref{eqn:layerPotential}, we the
upsampling rate given in Table~\ref{tbl:upsampling}.  For points that
are closer than $5/16$ of an arclength from $\bd\Omega$, a value of 0 is
simply assigned to $\phi$.

In future work, such as sedimenting eroding bodies, bodies will come too
close to one another for upsampling to only used.  Therefore, we plan to
implement a near-singular integration scheme that uses either
near-singular interpolation~\cite{qua-bir2014a}, quadrature by
expansion~\cite{klo-bar-gre-one2013}, Barycentric
interpolation~\cite{bar-wu-vee2015}, or panel-based
quadrature~\cite{hel-oja2008a}.

\begin{table}[htpb]
\centering
\begin{tabular}{|c|ccccc|}
  \hline
  $d(\xx,\bd\Omega)$ &
  $[5h,\infty]$ &
  $[\frac{5}{2}h,5h]$ &
  $[\frac{5}{4}h,\frac{5}{2}h]$ & 
  $[\frac{5}{8}h,\frac{5}{4}h]$ &
  $[\frac{5}{16}h,\frac{5}{8}h]$ \\ [2ex]
  \hline
  Upsample Rate & 1 & 2 & 4 & 8 & 16 \\
  \hline
\end{tabular}
\caption{\label{tbl:upsampling}The upsampling rate used in our
near-singular integration scheme.  $d(\xx,\bd\Omega)$ is the distance
between a points $\xx \in \Omega$ and the boundary of the domain
$\bd\Omega$, and $h$ is an arclength spacing.}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Accelerating the Layer Potential Evaluations}
To compute the velocity at an interior point $\xx \in \Omega$, the
integrand is periodic and smooth, so the trapezoid rule rule achieves
spectral accuracy.  Therefore, the velocity at a target points $\xx \in
\Omega$ is approximate by
\begin{align*}
  \uu(\xx) = \sum_{j=1}^N K(\xx,\xx_j) \eeta(\xx_j) \Delta s_j.
\end{align*}
If the velocity needs to be computed at $N_\tar$ points in $\Omega$,
where $N_\tar$ is large, the FMM is used to reduce the complexity from
$\bigO(N_\tar N)$ to $\bigO(N_\tar + N)$.

@@

@@
